Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-05-10 Moltres.tex
adds definitions for variable in diffusion eqn

Moltres \cite{lindsay_arfc/moltres_nodate} is implemented as an application for 
use atop the \gls{MOOSE} \cite{gaston_physics-based_2015} framework.

The Moltres code-base currently includes kernels and boundary conditions for
solving for neutron fluxes, temperature, and precursor concentrations. In \gls{MOOSE}
jargon, kernels are C++ classes that contain methods for computing residual and
Jacobian contributions corresponding to individual piecies of governing
equations. Developing the code-base in this way allows very modular construction
of equation systems; e.g. the same kernel that is used to represent heat
conduction can also be used to represent generic chemical diffusion. Moltres
also features neutron and precursor ``actions.'' These actions enable automatic
construction of the systems of equations for an arbitrary number of neutron and
precursor groups. This means that as long as group constants are provided in an appropriate
tabular form, a user only has to modify a couple of lines in a Moltres input
file to change from say two to fourty-four neutron groups.

@@

\begin{align}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'}
        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g 
        \nabla \phi_g + \Sigma_g^r \phi_g &= \sum_{g \ne g'}^G 
        \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - 
        \beta) \nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
\label{eq:neutrons}
        \intertext{where}
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>].
\end{align}

@@

\begin{align}
        \frac{\partial C_i}{\partial t} &= \sum_{g'= 1}^G \beta_i \nu 
        \Sigma_{g'}^f \phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u 
        C_i \label{eq:precursors}
        \intertext{where}
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
        <+var+> &= \mbox{<++>} [<+units+>]\\ 
\end{align}

>>>>

Moltres \cite{lindsay_arfc/moltres_nodate} is implemented as an application for 
use atop the \gls{MOOSE} \cite{gaston_physics-based_2015} framework. 
Accordingly, Moltres includes physics kernels and boundary conditions for
solving for neutron fluxes, temperature, and precursor concentrations. In \gls{MOOSE}
jargon, kernels are C++ classes that contain methods for computing residual and
Jacobian contributions corresponding to individual piecies of governing
equations. Developing the code-base in this way allows very modular construction
of equation systems; e.g. the same kernel that is used to represent heat
conduction can also be used to represent generic chemical diffusion. Moltres
also features neutron and precursor ``actions.'' These actions enable automatic
construction of the systems of equations for an arbitrary number of neutron and
precursor groups. This means that as long as group constants are provided in an appropriate
tabular form, a user only has to modify a couple of lines in a Moltres input
file to change from say two to fourty-four neutron groups.

@@

\begin{align}
%% \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
%% + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
%% \nu \Sigma_{g'}^f \phi_{g'}
        \frac{1}{v_g}\frac{\partial \phi_g}{\partial t} &- \nabla \cdot D_g 
        \nabla \phi_g + \Sigma_g^r \phi_g = \sum_{g \ne g'}^G 
        \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - 
        \beta) \nu \Sigma_{g'}^f \phi_{g'} + \chi_g^d \sum_i^I \lambda_i C_i
\label{eq:neutrons}
        \intertext{where}
        v_g &= \mbox{speed of neutrons in group g } [<+units+>]\\ 
        \phi_g &= \mbox{flux of neutrons in group g } [<+units+>]\\ 
        t &= \mbox{time } [<+units+>]\\ 
        D_g &= \mbox{Diffusion coefficient for neutrons in group g } [<+units+>]\\ 
        \Sigma_g^r &= \mbox{macroscopic cross-section for removal of neutrons 
        from group g } [<+units+>]\\ 
        \Sigma_{g'\rightarrow g} &= \mbox{macroscopic cross-section of 
        scattering from g' to g } [<+units+>]\\ 
        \chi_g^p &= \mbox{prompt fission spectrum, neutrons in group g } [<+units+>]\\ 
        G &= \mbox{number of discrete groups, g } [<+units+>]\\ 
        \nu &= \mbox{number of neutrons produced per fission } [<+units+>]\\ 
        \Sigma_g^f &= \mbox{macroscopic cross section for fission due to neutrons in group g } [<+units+>]\\ 
        \chi_g^d &= \mbox{delayed fission spectrum, neutrons in group g } [<+units+>]\\ 
        I &= \mbox{number of delayed neutron precursor groups } [<+units+>]\\ 
        \lambda_i &= \mbox{average decay constant of delayed neutron precursors 
        in precursor group i } [<+units+>]\\ 
        C_i &= \mbox{concentration of delayed neutron precursors in precursor 
        group i } [<+units+>]. 
\end{align}

@@

\begin{align}
        \frac{\partial C_i}{\partial t} &= \sum_{g'= 1}^G \beta_i \nu 
        \Sigma_{g'}^f \phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u 
        C_i \label{eq:precursors}
        \intertext{where}
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
        <+var+> &= \mbox{<+def+>} [<+units+>]\\ 
\end{align}
